Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-18 ms.qmd
Map working

ggplot() +
  geom_map(
    data = world_map, map = world_map,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray") +
  geom_point(
    data = all_pred,
    aes(long.x, lat.y, color = Estimate),
    alpha = 0.7
  ) +
  theme_void() +
  theme(legend.position = "none")

>>>>

ggplot() +
  geom_map(
    data = world_map, map = world_map,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray") +
  geom_point(
    data = all_pred,
    aes(long.x, lat.y, color = Estimate),
    alpha = 0.7, size = 6
  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$"))
